Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2013-11-13 writeups/proposal/proposal.tex
foo
Former-commit-id: 79beac62d9806c9ff092335339feec666e23fcfd [formerly d20e6e661561a3fa10520a9754093737d6ca6296]
Former-commit-id: 5c97b1e6eaa2b0cb9dc48f53056575489be90be1

When the system needed to recommend a set of individuals for a user to follow, it would take all of the words used in posts from that user to construct a search query to be provided to Lucene.
That search query would return the most likely users that share similar words in posts within their Twitter network with the words provided in the query.
Using this simple technique based on a standard text search engine allowed the recommendation system to accurately predict the people that a particular user follows at 25\% accuracy.

>>>>

When \citeauthor{Hannon2010}'s system recommended a set of individuals for a user to follow, it collected all of the words used in posts from that user, constructed a search query, and provided that query to Lucene.
Lucene then returned the most likely users that share similar words in posts within their Twitter network with the words provided in the query.
Using this simple technique based on a standard text search engine allowed the recommendation system to accurately predict the people that a particular user follows at 25\% accuracy.
